Preprocess

### 2024-04-16 src/preprocess.Rmd
Add 70+ for age ranges

```{r}
out <- out %>% mutate(
    age_range2 = case_when(
        age_unit == "Days" &
        age_value >= 0 &
        age_value <= 1 ~
            "0-1 Days",
        age_unit == "Days" &
        age_value >= 2 &
        age_value <= 6 ~
            "2-6 Days",
        age_unit == "Days" &
        age_value >= 7 &
        age_value <= 24 ~
            "7-24 Days",
        age_unit == "Years" &
        age_value >= 12 &
        age_value <= 24 ~
            "12-24",
        age_unit == "Years" &
        age_value >= 25 &
        age_value <= 39 ~
            "25-39",
        age_unit == "Years" &
        age_value >= 40 &
        age_value <= 54 ~
            "40-54",
        age_unit == "Years" &
        age_value >= 55 &
        age_value <= 69 ~
            "55-69",
        .default = NA
    ),
    .after = age_range
) %>%
    select(
        -age_value,
        -age_unit
    )

>>>>

```{r}
out <- out %>% mutate(
    age_range2 = case_when(
        age_unit == "Days" &
        age_value >= 0 &
        age_value <= 1 ~
            "0-1 Days",
        age_unit == "Days" &
        age_value >= 2 &
        age_value <= 6 ~
            "2-6 Days",
        age_unit == "Days" &
        age_value >= 7 &
        age_value <= 24 ~
            "7-24 Days",
        age_unit == "Years" &
        age_value >= 12 &
        age_value <= 24 ~
            "12-24",
        age_unit == "Years" &
        age_value >= 25 &
        age_value <= 39 ~
            "25-39",
        age_unit == "Years" &
        age_value >= 40 &
        age_value <= 54 ~
            "40-54",
        age_unit == "Years" &
        age_value >= 55 &
        age_value <= 69 ~
            "55-69",
        age_unit == "Years" &
        age_value >= 70 ~
            "70+",
        .default = NA
    ),
    .after = age_range
) %>%
    select(
        -age_value,
        -age_unit
    )
